Cover Letter: Cudele

### 2017-12-29 paper/cover_letter.tex
paper: #41 and #34
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\begin{document}
\title{Cover Letter}
\maketitle

We thank the reviewers for their hard work and genuinely helpful suggestions.
In addition to this cover letter, we have posted a PDF online explicitly
showing additions in \textcolor{red}{\textbf{red}} and deletions in
\textcolor{blue}{\textbf{blue}}. Three issues were common across reviewer
feedback; Reviewer 1 and 3's comments are addressed in issues I and II,
Reviewer 2's comments are addressed in issues I and III, and Reviewer 4's
comments are addressed in issues II and III.

%Use Cases R2, R4
%- Spark discussion R2
%- more emphasis on parallel and distributed computing themes R4
\section*{Issue I: Synthetic and/or Irrelevant Use Cases (Reviewers 2 and 4)}

To show the relevance of the use cases, we re-wrote Section~{\S}V-B to
highlight examples from HPC and cloud workloads that would benefit from using
Cudele. For HPC we focus on user home directories used for experiments and for
the cloud we focus on the Hadoop and Spark runtimes (as suggested by Reviewer
2). To connect the problematic use cases to Cudele, we added \textbf{Cudele
setup} headers in Section~{\S}V-B to show which subtree semantics accomodate
these workloads in the global namespace.  By showing these setups, we hope to
demonstrate that different applications can use a file system in parallel with
different consistency/durability semantics.  Although we do not actually run
the workloads on our prototype, hopefully our changes show how the use cases,
and the synthetic benchmarks we used to represent them, are indeed relevant to
parallel and distributed computing.

To align the paper to the themes of the conference, we changed Section~{\S}V-A
and Figures 6a, 6b, and 6c to emphasize that decoupled namespaces facilitate
client-driven parallelism. Clients detach subtrees form the global namespaces
and do operations in-parallel to their local disk. We also hope that changes to
the use cases above motivates the need for robust distributed storage systems
that can handle today's applications.  So while the paper is storage-centric,
we try to show that the workloads it supports are highly distributed and need a
flexible solution like Cudele.

@@

All reviewers note that the results and contributions we cite in the
introduction are not validated, explained, or even mentioned in the evaluation.
One confusing component of this issue is that we mixed future work with the
contributions of the paper; to make the contributions more explicit we remove
future work from the introduction and add it to Section~{\S}VI; we do not
attempt to validate or prove any of the statements about the benefits of
changing consistency and durability properties of a subtree dynamically, such
as saving resource provisioning costs.  To further clarify the evaluation, we:

@@

  \item explicitly state the Cudele setups and subtree configurations in bold
in Section~{\S}V-A. Hopefully this helps the reader keep track of use cases and
demonstrates how Cudele might be able to help in these scenarios.

and include baseline values in the
text so readers can quickly calculate raw numbers from our speedup/slowdown
graphs. We also make sure to connect all speedups from the introduction to the
evaluation. We hope this clarifies confusion about what we are comparing to
when we reference speedups and slowdowns.

  \item re-organized the sections and removed cross-references. Experiments are
now self-contained so the reader can see the effects of different API
configurations and we do a better job of explaining how results are derived.

  \item removed the ``major takeaways". We deleted the headings but moved the
text to the beginning of each section to motivate why we are doing each
experiment.  We also add insights into the results by analyzing the raw numbers
we observe in comparison to hardware capabilities.

  \item re-labeled all graphs with the same metric (throughput
slowdown/speedup) and aligned Section~{\S}V with the graphs in Section~{\S}II.
We hope this eliminates more of the confusion triggered by the
cross-referencing we did, referenced by Reviewers 2 and 3.

@@

We apologize for the omission of experimental setup and source code details. To
provide a more comprehensive view of our experiments, we added text to the
paper and made paper artifacts available online. For the experimental setup, we
describe the cluster setup (hardware, software, etc.) in Section~{\S}V.  We
have also made the infrastructure code available and added links after each
figure to show exactly how experiments are run.  This infrastructure code
contains scripts to deploy the system, run experiments, and gather results.
This process follows the Popper
Convention\footnote{http://falsifiable.us/}~\cite{jimenez_popper_2016}, which
aims to make research reproducible.  We also made the source code available
online and a link is provided in a footnote in Section~{\S}V. Finally, we add
details about which tools and classes we modified in Section~{\S}IV to address
Reviewer 1's questions about the framework implementation.

\section*{Cosmetic Fixes}
%Terminology
%- users vs. clients R2
\begin{itemize}
  \item Reviewer 1: fixed user vs. client terminology in Section~{\S}III
  \item Reviewer 1: clarified that the cost of dynamically changing semantics is future work Sections~{\S}III and ~{\S}V.E
  \item Reviewer 1: added source code pointer in Section~{\S}IV
  \item Reviewer 2: remove major takeways in Section~{\S}V
  \item Reviewer 2: remove major cross-references in Section~{\S}V
  \item Reviewer 3: quantified speedups with figure annotations in Section~{\S}V
  \item Reviewers 1 and 3: add servers, network, and storage setups in Section~{\S}V
  \item Reviewer 4: add new section ({\S}V.F) describing how Cudele would work with a system like Spark
\end{itemize}

>>>>

\begin{document}
\title{Cover Letter: Cudele}
\maketitle

We thank the reviewers for their hard work and genuinely helpful suggestions.
In addition to this cover letter, we have posted a PDF online explicitly
showing additions in \textcolor{red}{\textbf{red}} and deletions in
\textcolor{blue}{\textbf{blue}}. Three issues were common across reviewer
feedback; Reviewer 1 and 3's comments are addressed in issues II and III,
Reviewer 2's comments are addressed in issues I and III, and Reviewer 4's
comments are addressed in issues I and II.

%Use Cases R2, R4
%- Spark discussion R2
%- more emphasis on parallel and distributed computing themes R4
\section*{Issue I: Irrelevant and/or Synthetic Use Cases (Reviewers 2 and 4)}

We re-wrote Section~{\S}V-B to highlight examples from HPC and cloud workloads
that would benefit from using Cudele. For HPC we focus on user home directories
used for experiments and for the cloud we focus on the Hadoop and Spark
runtimes (as suggested by Reviewer 2).  We also added \textbf{In Cudele}
headers in Section~{\S}V-B to show which subtree semantics accommodate each
workload and to demonstrate how Cudele might be able to help in these
scenarios.  By showing these setups, we hope to demonstrate that different
applications can use a file system in parallel with different
consistency/durability semantics.  Although we do not actually run the
workloads on our prototype, hopefully our changes show how the use cases, and
the synthetic benchmarks we used to represent them, are indeed relevant to
parallel and distributed computing.

To align the paper to the themes of the conference, we changed Section~{\S}V-A
and Figures 6a, 6b, and 6c to emphasize that decoupled namespaces facilitate
client-driven parallelism, where clients detach subtrees form the global namespaces
and do operations in-parallel to their local disk. We also hope that changes to
the use cases above motivates the need for robust distributed storage systems
that can handle today's applications.  So while the paper is storage-centric,
we try to show that the workloads it supports are highly distributed and need a
flexible solution like Cudele.

@@

To clarify the evaluation and eliminate some of the confusion due to our
cross-referencing, we:

@@

  \item connected performance gains from the abstract and Section~{\S}I to
Section~{\S}V to clarify speedup/slowdown comparisons and to show how results
are derived; we also re-labeled all graphs with the same metric (throughput
slowdown/speedup) and aligned Section~{\S}V with the graphs in Section~{\S}II.

  \item made experiments self-contained in Sections~{\S}II and~{\S}V by
removing cross-references and adding baseline values so readers can calculate
raw numbers from our speedup/slowdown graphs.

  \item explicitly state Cudele setups and subtree configurations in bold in
Section~{\S}V-B to guide the reader through use cases and the effects of
different Cudele API configurations.

  \item removed ``major takeaways" from Section~{\S}V and focused on
insights into results by analyzing raw numbers in comparison to hardware
speeds.

  \item removed future work from Section~{\S}I to make the contributions
explicit. We do not attempt to validate or prove any of the statements about
the benefits of changing consistency and durability properties of a subtree
dynamically, such as saving resource provisioning costs.

  \item clarified confusing terminology in Section~{\S}II: administrator refers
to a person that configures subtrees and client refers to a storage client or
application that interacts with the metadata server. We avoid using the term
``user" except when referring to end-users that interact with home directories
in a file system or the Hadoop/Spark runtime itself.

@@

We apologize for the omission of experimental setup and source code details.
We made artifacts available online for all experiments in the paper. For the
experimental setup, we describe the cluster setup (hardware, software, etc.) in
Section~{\S}V.  We have also made the infrastructure code available and added
links after each figure to show exactly how experiments are run.  This
infrastructure code contains scripts to deploy the system, run experiments, and
gather results.  This process follows the Popper
Convention\footnote{http://falsifiable.us/}~\cite{jimenez_popper_2016}, which
aims to make research reproducible.  We also made the source code available
online and a link is provided in a reference in Section~{\S}V. Finally, we add
details about which tools and classes we modified in Section~{\S}IV to address
Reviewer 1's questions about the framework implementation.

%\section*{Cosmetic Fixes}
%%Terminology
%%- users vs. clients R2
%\begin{itemize}
%  \item Reviewer 1: fixed user vs. client terminology in Section~{\S}III
%  \item Reviewer 1: clarified that the cost of dynamically changing semantics is future work Sections~{\S}III and ~{\S}V.E
%  \item Reviewer 1: added source code pointer in Section~{\S}IV
%  \item Reviewer 2: remove major takeways in Section~{\S}V
%  \item Reviewer 2: remove major cross-references in Section~{\S}V
%  \item Reviewer 3: quantified speedups with figure annotations in Section~{\S}V
%  \item Reviewers 1 and 3: add servers, network, and storage setups in Section~{\S}V
%  \item Reviewer 4: add new section ({\S}V.F) describing how Cudele would work with a system like Spark
%\end{itemize}

### 2017-12-29 paper/sections/0_abstract.tex
paper: #41 and #34
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

HPC and data center scale application developers are abandoning POSIX IO
because the file system metadata synchronization and serialization overheads of
providing strong consistency and durability are too costly -- and often
unnecessary -- for their applications.  Unfortunately, designing file systems
with weaker consistency or durability excludes applications that rely on
stronger guarantees, forcing developers to re-write their applications or
deploy them on a different system.  Users can mount multiple systems in the
global namespace but this means (1) provisioning separate storage clusters and
(2) manually moving data across system boundaries.  We present a framework and
API that lets clients specify their consistency/durability requirements and
dynamically assign them to subtrees in the same namespace, allowing users to
optimize subtrees over time and space for different workloads.  We confirm the
performance benefits of techniques presented in related work but also explore
new consistency/durability metadata designs, all integrated over the same
storage system.  By custom fitting a subtree to a create-heavy application, we
show similar speedups to related work \newcomment{but more importantly, our
prototype can custom fit subtrees in the same namespace to applications common
in large data centers, such as checkpoint-restart (91.7\(\times\), user home
directories (within a 0.03 standard deviation from optimal), and clients
checking for partial results (only a 2\% overhead).}  \oldcomment{ and can
scale to 2\(\times\) as many clients when compared to our baseline system.}

@@

>>>>

HPC and data center scale application developers are abandoning POSIX IO
because file system metadata synchronization and serialization overheads of
providing strong consistency and durability are too costly -- and often
unnecessary -- for their applications.  Unfortunately, designing file systems
with weaker consistency or durability excludes applications that rely on
stronger guarantees, forcing developers to re-write their applications or
deploy them on a different system.  We present a framework and API that lets
\oldcomment{clients}\newcomment{administrators} specify their
consistency/durability requirements and dynamically assign them to subtrees in
the same namespace, allowing administrators to optimize subtrees over time and
space for different workloads. \oldcomment{By custom fitting a subtree to a
create-heavy application,} We show similar speedups to related work but more
importantly, \oldcomment{our prototype can custom fit subtrees in the same
namespace to applications common in large data centers, }\newcomment{ we show
performance improvements when we custom fit subtree semantics to applications}
such as checkpoint-restart (91.7\(\times\) speedup), user home directories
(0.03 standard deviation from optimal), and
\oldcomment{clients}\newcomment{users} checking for partial results (2\%
overhead). \oldcomment{ and can scale to 2\(\times\) as many clients when
compared to our baseline system.}

@@

%Users can mount multiple systems in the
%global namespace but this means (1) provisioning separate storage clusters and
%(2) manually moving data across system boundaries.

%We confirm the performance benefits of
%techniques presented in related work but also explore new
%consistency/durability metadata designs, all integrated over the same storage
%system.

### 2017-12-29 paper/sections/1_introduction.tex
paper: #41 and #34
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

% What is the problem?
File system metadata services in HPC and large-scale data centers have
scalability problems because common tasks, like
checkpointing~\cite{bent_plfs_2009} or scanning the file
system~\cite{zheng:pdsw2014-batchfs}, contend for the same directories and
inodes. Applications perform better with dedicated metadata
servers~\cite{sevilla:sc15-mantle, ren:sc2014-indexfs} but provisioning a
metadata server for every \newcomment{client\footnote{In this paper, ``client"
is a storage client or application that interacts with the metadata server,
``administrator" is a system administrator that configures the storage, and
``end-users" interact with the file system, via home directories or runtimes.}}
is unreasonable. This problem is exacerbated by current hardware and software
trends: parallel runtimes like Hadoop and Spark use storage systems to
implement important scheduling and timing semantics, and  \oldcomment{; for
example, } HPC architectures are transitioning from complex storage stacks with
burst buffer, file system, object store, and tape tiers to more simplified
stacks with just a burst buffer and object
store~\cite{bent:login16-hpc-trends}. These types of trends put pressure on
data access because more requests from different nodes end up hitting the same
layer in parallel and latencies cannot be hidden while data migrates across
tiers.

@@

\begin{figure}[tb] \centering
\includegraphics[width=0.35\textwidth]{figures/subtree-policies1.png}
\caption{Illustration of subtrees with different semantics co-existing in a
global namespace.  For performance, clients \oldcomment{can} relax consistency on their
subtree (HDFS) or decouple the subtree and move it locally (BatchFS, RAMDisk).
Decoupled subtrees can relax durability for even better performance.
}\label{fig:subtree-policies} \end{figure}

@@

% What did we do
To address this problem, we present an API and framework that lets developers
dynamically control the consistency and durability guarantees for subtrees in
the file system namespace.  Figure~\ref{fig:subtree-policies} shows a potential
setup in our proposed system where a single global namespace has subtrees for
applications optimized with techniques from different state-of-the-art
architectures.  The HDFS\footnote{HDFS itself is not directly evaluated in this
paper, although the semantics and their performance is explored
in~\S\ref{sec:use-case-1}.} subtree has weaker than strong consistency because
it lets clients read files opened for
writing~\cite{hakimzadeh:dais14-hdfs-consistency}, which means that not all
updates are immediately seen by all clients; the BatchFS and RAMDisk subtrees
are decoupled from the global namespace and have similar consistency/durability
behavior to those systems; and the POSIX IO subtree retains the rigidity of
POSIX IO's strong consistency.  Subtrees without policies inherit the
consistency/durability semantics of the parent and future work will examine
embeddable or inheritable policies.

@@

  \item A framework and API for assigning consistency/durability policies to
  subtrees in the file system namespace; this lets
  \oldcomment{users}\newcomment{administrators} navigate the trade-offs of
  different metadata protocols on the same storage system.

  \item This framework lets subtrees with different semantics co-exist in a
  global namespace. We show how this scales further and performs better than
  systems that use one strategy for the entire namespace .

>>>>

% What is the problem?
File system metadata services in HPC and large-scale data centers have
scalability problems because common tasks, like
checkpointing~\cite{bent_plfs_2009} or scanning the file
system~\cite{zheng:pdsw2014-batchfs}, contend for the same directories and
inodes. Applications perform better with dedicated metadata
servers~\cite{sevilla:sc15-mantle, ren:sc2014-indexfs} but provisioning a
metadata server for every \newcomment{client} is unreasonable. This problem is
exacerbated by current hardware and software trends: parallel runtimes like
Hadoop and Spark use storage systems to implement important scheduling and
timing semantics, and  \oldcomment{; for example, } HPC architectures are
transitioning from complex storage stacks with burst buffer, file system,
object store, and tape tiers to more simplified stacks with just a burst buffer
and object store~\cite{bent:login16-hpc-trends}. These types of trends put
pressure on data access because more requests from different nodes end up
hitting the same layer in parallel and latencies cannot be hidden while data
migrates across tiers.

@@

\begin{figure}[tb] \centering
\includegraphics[width=0.35\textwidth]{figures/subtree-policies1.png}
\caption{Illustration of subtrees with different semantics co-existing in a
global namespace.  For performance, clients \oldcomment{can} relax consistency/durability on their
subtree ({\it e.g.}, HDFS) or decouple the subtree and move it locally ({\it e.g.}, BatchFS, RAMDisk).
}\label{fig:subtree-policies} \end{figure}

@@

% What did we do
%\footnote{HDFS itself is not directly evaluated in this paper, although the
%semantics and their performance is explored in~\S\ref{sec:use-case-1}.} 
To address this problem, we present an API and framework that lets developers
dynamically control the consistency and durability guarantees for subtrees in
the file system namespace.  Figure~\ref{fig:subtree-policies} shows a potential
setup in our proposed system where a single global namespace has subtrees for
applications optimized with techniques from different state-of-the-art
architectures.  The HDFS subtree has weaker than strong consistency because it
lets clients read files opened for
writing~\cite{hakimzadeh:dais14-hdfs-consistency}, which means that not all
updates are immediately seen by all clients; the BatchFS and RAMDisk subtrees
are decoupled from the global namespace and have similar consistency/durability
behavior to those systems; and the POSIX IO subtree retains the rigidity of
POSIX IO's strong consistency.  Subtrees without policies inherit the
consistency/durability semantics of the parent and future work will examine
embeddable or inheritable policies.

@@

  \item A framework/API for assigning consistency/durability policies to
  subtrees in a global namespace; this lets
  \oldcomment{users}\newcomment{administrators} navigate trade-offs of
  different metadata protocols on the same storage system.

  \item

  \oldcomment{This framework lets subtrees with different semantics co-exist in
a global namespace. We show how this} \newcomment{We show how that letting
different semantics co-exist in a global namespace scales further and performs
better than systems that use one strategy.}

### 2017-12-29 paper/sections/3_posix_overheads.tex
paper: #41 and #34
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\begin{figure}[tb] \centering
\includegraphics[width=1\linewidth]{./graphs/overhead-creates.png}
\caption{[\href{https://github.com/michaelsevilla/cudele-popper/blob/revision/experiments/baseline-compile/visualize/viz.ipynb}{source}]
For the CephFS metadata server, create-heavy workloads ({\it e.g.},
\texttt{untar}) incur the highest disk, network, and CPU utilization because of
the consistency and durability demands of CephFS.}\label{fig:overhead-creates}
\end{figure}

In our examination of the overheads of POSIX IO we benchmark and analyze
CephFS, the file system that uses Ceph's object store ({\it i.e.} RADOS) to
store its data and metadata. To show how the file system behaves under high
metadata load we use a create-heavy workload.  During this process we
discovered, based on the analysis and breakdown of costs, that durability and
consistency have high overhead but we urge the reader to keep in mind that this
file system is an implementation of one set of design decisions and our goal
here is to highlight the effect that those decisions have on performance.

>>>>

\begin{figure}[tb] \centering
\includegraphics[width=1\linewidth]{./graphs/overhead-creates.png}
\caption{[\href{https://github.com/michaelsevilla/cudele-popper/blob/revision/experiments/baseline-compile/visualize/viz.ipynb}{source}]
For the CephFS metadata server, create-heavy workloads ({\it e.g.},
\texttt{untar}) incur the highest disk, network, and CPU utilization because of
consistency/durabiliy demands.}\label{fig:overhead-creates}
\end{figure}

In our examination of the overheads of POSIX IO we benchmark and analyze
CephFS, the file system that uses Ceph's object store ({\it i.e.} RADOS) to
store its data and metadata. \newcomment{In this paper, ``client" is a storage
client or application that interacts with the metadata server, ``administrator"
is a system administrator that configures the storage, and ``end-users"
interact with the file system, via home directories or runtimes.} To show how
the file system behaves under high metadata load we use a create-heavy
workload.  During this process we discovered, based on the analysis and
breakdown of costs, that durability and consistency have high overhead but we
urge the reader to keep in mind that this file system is an implementation of
one set of design decisions and our goal here is to highlight the effect that
those decisions have on performance.

### 2017-12-29 paper/sections/4_methodology.tex
paper: #41 and #34
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\begin{figure}[tb]
\centering
\includegraphics[width=90mm]{figures/fig-decouple.png}
\caption{Illustration of the \textbf{mechanisms} used by applications to build
consistency/durability semantics. Descriptions are provided in
Table~\ref{table:mechanisms} and the underlined words in
Section~\S\ref{sec:the-cudelesfs-mechanisms}.}\label{fig:decouple}
\end{figure}

\begin{table}
\begin{tabular}{ r | l }
  Mechanism         & Description \\\hline
  RPCs              & round trip remote procedure calls \\
  Stream            & stream journal into object store \\
  Append Client Journal & events appended to in-memory journal \\
  Volatile Apply & apply to metadata store in memory \\
  Nonvolatile Apply    & apply to metadata store in obj store \\
  Local Persist     & journal saved to client's disk \\
  Global Persist    & journal saved in object store \\
\end{tabular}
\caption{Descriptions of the mechanisms. Example compositions are shown in Table~\ref{table:spectrum}.\label{table:mechanisms}} 
\end{table}

@@

% describe the figure
Figure~\ref{fig:decouple} shows the mechanisms (labeled arrows) in Cudele and
which daemon(s) they are performed by.  Table~\ref{table:mechanisms} has a
description of what each mechanism does.  Decoupled clients use the
\underline{Append Client Journal} mechanism to append metadata updates to a
local, in-memory journal. Clients do not need to check for
consistency when writing events and the metadata server blindly applies the
updates because it assumes the events were already checked for consistency. The
trade-off here is fast performance; it is a dangerous approach but could be
implemented safely if the clients or metadata server are configured to check
the validity of events before writing them.  Once the job is complete, the
system calls mechanisms to achieve the desired consistency/durability
semantics.  Cudele provides a library for clients to link into and all
operations are performed by the client.

@@

% which system they represent and which are impossible
Existing, state-of-the-art systems in HPC can be represented by the cells in
Table~\ref{table:spectrum} (we construct the semantics for these systems later
in Section~\S\ref{sec:microbenchmarks}).  POSIX IO-compliant systems like
CephFS and IndexFS have global consistency and durability\footnote{This is the
normal case.  IndexFS also has bulk merge which would transition the system
into ``weak consistency"}; DeltaFS uses ``invisible" consistency and ``local"
durability and BatchFS uses ``weak" consistency and ``local" durability. These
systems have other features that could push them into different semantics but
we assign labels here based on the points emphasized in the papers.  To compose
the mechanisms \oldcomment{users}\newcomment{administrators} inject which
mechanisms to run and which to use in parallel using a domain specific
language.  Although we can achieve all permutations of the different guarantees
in Table~\ref{table:spectrum}, not all of them make sense. For example, it
makes little sense to do \texttt{append client journal+RPCs} since both
mechanisms do the same thing or \texttt{stream+local persist} since ``global"
durability is stronger and has more overhead than ``local" durability. The cost
of each mechanism and the semantics described above are quantified in
Sections~\S\ref{sec:microbenchmarks} and~\S\ref{sec:use-case-1}.

@@

% the interface
Users control consistency and durability for subtrees by contacting a daemon in
the system called a monitor, which manages cluster state changes.  Users
present a directory path and a policies configuration that gets distributed and
versioned by the monitor to all daemons in the system. For example,
(msevilla/mydir, policies.yml) would decouple the path ``msevilla/mydir" and
would apply the policies in ``policies.yml".  The policies file supports the
following parameters (default values are in parenthesis):

\begin{itemize}

  \item \texttt{consistency}: which consistency model to use (\texttt{RPCs})

  \item \texttt{durability}: which durability model to use (\texttt{stream})

  \item \texttt{allocated\_inodes}: the number of inodes to provision to the
  decoupled namespace (100)

  \item \texttt{interfere\_policy}: how to handle a request from another
  client targeted at this subtree (\texttt{allow})

\end{itemize}

The ``Consistency" and ``Durability" parameters are compositions of mechanisms;
they can be serialized (\(+\)) or run in parallel (\(|\|\)).  ``Allocated
Inodes" is a way for the application to specify how many files it intends to
create. It is a contract so that the file system can provision enough resources
for the incumbent merge and so it can give valid inodes to other clients. The
inodes can be used anywhere within the decoupled namespace ({i.e.} at any depth
in the subtree).  ``Interfere Policy" has two settings: \texttt{block} and
\texttt{allow}.  For \texttt{block}, any requests to this part of the namespace
returns with ``Device is busy", which will spare the metadata server from
wasting resources for updates that may get overwritten. If the application does
not mind losing updates, for example it wants approximations for results that
take too long to compute, it can select \texttt{allow}. In this case, metadata
from the interfering client will be written and the computation from the
decoupled namespace will take priority at merge time because the results are
more accurate.  Given these default values decoupling the namespace with an
empty policies file would give the application 100 inodes but the subtree would
behave like the existing CephFS implementation.

>>>>

\begin{figure}[tb]
\centering
%\includegraphics[width=50mm]{figures/fig-decouple.png}
\includegraphics[width=1.0\linewidth]{figures/fig-decouple.png}
\caption{Illustration of the \textbf{mechanisms} used by applications to build
consistency/durability semantics. Descriptions are provided in by the
underlined words in Section~\S\ref{sec:the-cudelesfs-mechanisms}.
}\label{fig:decouple}
\end{figure}

%\begin{table}
%\begin{tabular}{ r | l }
%  Mechanism         & Description \\\hline
%  RPCs              & round trip remote procedure calls \\
%  Stream            & stream journal into object store \\
%  Append Client Journal & events appended to in-memory journal \\
%  Volatile Apply & apply to metadata store in memory \\
%  Nonvolatile Apply    & apply to metadata store in obj store \\
%  Local Persist     & journal saved to client's disk \\
%  Global Persist    & journal saved in object store \\
%\end{tabular}
%\caption{Descriptions of the mechanisms. Example compositions are shown in Table~\ref{table:spectrum}.\label{table:mechanisms}} 
%\end{table}

@@

% describe the figure
Figure~\ref{fig:decouple} shows the mechanisms (labeled arrows) in Cudele and
which daemon(s) they are performed by. \oldcomment{Table~\ref{table:mechanisms} has a
description of what each mechanism does.}  Decoupled clients use the
\underline{Append Client Journal} mechanism to append metadata updates to a
local, in-memory journal. Clients do not need to check for
consistency when writing events and the metadata server blindly applies the
updates because it assumes the events were already checked for consistency. The
trade-off here is fast performance; it is a dangerous approach but could be
implemented safely if the clients or metadata server are configured to check
the validity of events before writing them.  Once the job is complete, the
system calls mechanisms to achieve the desired consistency/durability
semantics.  Cudele provides a library for clients to link into and all
operations are performed by the client.

@@

% which system they represent and which are impossible
Existing, state-of-the-art systems in HPC can be represented by the cells in
Table~\ref{table:spectrum} (we construct the semantics for these systems later
in Section~\S\ref{sec:microbenchmarks}).  POSIX IO-compliant systems like
CephFS and IndexFS have global consistency and durability\footnote{ IndexFS
also has bulk merge which is a form of ``weak consistency"}; DeltaFS uses
``invisible" consistency and ``local" durability and BatchFS uses ``weak"
consistency and ``local" durability. These systems have other features that
could push them into different semantics but we assign labels here based on the
points emphasized in the papers.  To compose the mechanisms
\oldcomment{users}\newcomment{administrators} inject which mechanisms to run
and which to use in parallel using a domain specific language.  Although we can
achieve all permutations of the different guarantees in
Table~\ref{table:spectrum}, not all of them make sense. For example, it makes
little sense to do \texttt{append client journal+RPCs} since both mechanisms do
the same thing or \texttt{stream+local persist} since ``global" durability is
stronger and has more overhead than ``local" durability. The cost of each
mechanism and the semantics described above are quantified in
Sections~\S\ref{sec:microbenchmarks} and~\S\ref{sec:use-case-1}.

@@

% the interface
Users control consistency and durability for subtrees by contacting a daemon in
the system called a monitor, which manages cluster state changes.  Users
present a directory path and a policies configuration that gets distributed and
versioned by the monitor to all daemons in the system. For example,
(msevilla/mydir, policies.yml) would decouple the path ``msevilla/mydir" and
would apply the policies in ``policies.yml".  The policies file supports the
following parameters (default values are in parenthesis): which consistency
model to use (\texttt{RPCs}), which durability model to use (\texttt{stream})
number of inodes to provision to the decoupled namespace (100), which interfere
policy to use, {\it i.e.} how to handle a request from another client
targeted at this subtree (\texttt{allow}). The ``Consistency" and ``Durability"
parameters are compositions of mechanisms; they can be serialized (\(+\)) or
run in parallel (\(|\|\)).  ``Allocated Inodes" is a way for the application to
specify how many files it intends to create. It is a contract so that the file
system can provision enough resources for the incumbent merge and so it can
give valid inodes to other clients. The inodes can be used anywhere within the
decoupled namespace ({i.e.} at any depth in the subtree).  ``Interfere Policy"
has two settings: \texttt{block} and \texttt{allow}.  For \texttt{block}, any
requests to this part of the namespace returns with ``Device is busy", which
will spare the metadata server from wasting resources for updates that may get
overwritten. If the application does not mind losing updates, for example it
wants approximations for results that take too long to compute, it can select
\texttt{allow}. In this case, metadata from the interfering client will be
written and the computation from the decoupled namespace will take priority at
merge time because the results are more accurate.  Given these default values
decoupling the namespace with an empty policies file would give the application
100 inodes but the subtree would behave like the existing CephFS
implementation.
